---
title: "Customer Segmentation"
author: "YI-LING HUANG"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
library(dplyr)
library(VIM)
library(ggplot2)
library(factoextra)
library(psych)
```

```{r}
a <- read.csv("Mall_Customers.csv")
```

```{r}
a$CustomerID <- as.factor(a$CustomerID)
```

# Data preparation
```{r}
aggr(a)
# shows dataset has no missing value
```

# Normalize data
```{r}
a_m <- a
a_m$Age <- scale(a$Age)
a_m$Annual.Income..k.. <- scale(a$Annual.Income..k..)
a_m$Spending.Score..1.100. <- scale(a$Spending.Score..1.100.)

```

# (1) How to find optimal k (elbow method)
```{r}
kmean_withinss <- function(k) {
    cluster <- kmeans(a_m[,3:5], k)
    return (cluster$tot.withinss)
}

# Set maximum cluster 
max_k <-20 
# Run algorithm over a range of k 
wss <- sapply(2:max_k, kmean_withinss)

# Create a data frame to plot the graph
elbow <-data.frame(2:max_k, wss)
```

# Graph to visualize where is the elbow point
```{r}
ggplot(elbow, aes(x = X2.max_k, y = wss)) +
    geom_point() +
    geom_line() +
    scale_x_continuous(breaks = seq(1, 20, by = 1))
```

When k is 8, the curve is starting to have a diminishing tendency.


# (2) How to find optimal k (Average Silhouette Method)
```{r}
x <- fviz_nbclust(x = a_m[,3:5],FUNcluster = kmeans, method = 'silhouette' )
x
```

Average Silhouette Method also suggests that 8 is the optimal value for k.

# View clusters
```{r}
set.seed(123)
cluster_8 <-kmeans(a_m[,3:5], 8)
cluster_8
```

```{r}
cluster_8$centers
cluster_8$size
```

# Visualize clusters with graph
```{r}
fviz_cluster(cluster_8, data = a_m[,3:5])
```

# Add cluster to original dataset and do descriptive analysis by groups
```{r}
b <- a %>% 
  mutate(Cluster = cluster_8$cluster)
b$Cluster <- as.factor(b$Cluster)
b <- b %>%
  select(-c(CustomerID))

describe.by(b, group = b$Cluster)
```

# Plot variables based on groups
```{r}
# Age
ggplot(b, aes(x=Cluster, y=Age, fill=Cluster)) + 
    geom_boxplot()+
    ggtitle("Age by Cluster")

# Annual.Income..k..
ggplot(b, aes(x=Cluster, y=Annual.Income..k.., fill=Cluster)) + 
    geom_boxplot()+
    ggtitle("Annual Income by Cluster")

# Spending.Score..1.100.
ggplot(b, aes(x=Cluster, y=Spending.Score..1.100., fill=Cluster)) + 
    geom_boxplot()+
    ggtitle("Spending Score by Cluster")

# Gender
b %>%
  select(Gender, Cluster) %>%
  group_by(Cluster, Gender) %>%
  summarise(cnt = n()) %>%
  ggplot(aes(x = Cluster, y = cnt, fill = Gender))+
  geom_bar(stat="identity", position=position_dodge())

```

